### 2011-09-29 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

@@

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková Ph.D.}
\def\mfplacedate{Praha, 2011}

@@

Vedoucí diplomové práce: \mfadvisor{}, Katedra softwarového inženýrství

@@

As usual, source code excerpts, class, field and method names shall be written in fixed-width font, such as \texttt{getHeuristic()}. Names of specific heuristics will be written like this: \heu{Mutation}. Name of test data sets will be written like this: \dataset{OVA1}.\\

>>>>

% TODO uncomment this to get much shorter ToC
% \setcounter{tocdepth}{1}

@@

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Ire\-na Mlýn\-ko\-vá Ph.D.}
\def\mfplacedate{Praha, 2011}

@@

Vedoucí diplomové práce: \mfadvisor{}, Ka\-ted\-ra soft\-wa\-ro\-vé\-ho in\-že\-nýr\-ství

@@

As usual, source code excerpts, class, field and method names shall be written in fixed-width font, such as \texttt{get\-Heu\-ris\-tic()}. Names of specific heuristics will be written like this: \heu{Mutation}. Name of test data sets will be written like this: \dataset{OVA1}.\\
